Many Analystis Project

### 2022-02-18 analysis-v-2.Rmd
update analysis

```{r runanalysis, echo=FALSE, include = FALSE}
# source("libs.R") # libraries 
# source("funs.R") # custom functions
library("tidyverse")
library("easystats")
library("ggplot2") #plots
library("sjstats") #test statistics
library("sjPlot")
library("sjmisc")
library("insight")
library("see")
library("performance")
library("ggraph")
library("parameters")
library("lme4")
library("psych") ## correlation matrix
library("table1")
library("ggeffects")
library("gghighlight")
library("texreg")
library("kableExtra")
#library("naniar") # missingness
#library("Amelia")
#library("magrittr")
library("patchwork")
library("texreg")
library("viridisLite")
library("patchwork")
library("here")
#library("rethinking")
#library("statsExpressions")
#library("ggstatsplot")
library("ggthemes")
library("ggdag")
library("rstan")
library("brms")
library("tidybayes")
library("bayesplot")
library("dagitty")
library("ggdag")
library("geepack")  # marginal structural models
library("ipw") # inverse probability weighting. 
library("WeightIt")# inverse probability weighting. 
rstan_options(auto_write=TRUE)
options(mc.cores=parallel::detectCores ())
theme_set(theme_few())
```

@@

```{r}
# get data into shape
d1 <- df %>%
  dplyr::filter(
    !is.na(wb_psychANXIETY),
    !is.na(age),
    !is.na(rel_CHURCHFREQ),
   # !is.na(wb_psychMEANING),
    !is.na(male),
    !is.na(rel_EXTENTBELIEVEGOD),
  ) %>%
  dplyr::mutate(
    anx = as.integer(6- wb_psychANXIETY), # reverse coded! rescale 1-5
    anx_s = scale(anx),
    #put outcome in ST units (see McElreath 2021)  # not necessary
    age_s = scale(age),
    ch = rel_CHURCHFREQ,
    mn  = wb_psychMEANING,
    bg =  rel_EXTENTBELIEVEGOD,
    ch_s = scale(rel_CHURCHFREQ),
    mn_s = scale(wb_psychMEANING),
    bg_s = scale(rel_EXTENTBELIEVEGOD)
  ) %>%
  dplyr::select(anx,
                ch,
                mn,
                bg,
                anx_s,
                age_s,
                ch_s,
                mn_s,
                male2,
                country,
                male,
                bg_s,
                wb_psychANXIETY)

## degroup variables for within and between analysis
## https://cran.r-project.org/web/packages/parameters/vignettes/demean.html
d1 <-
  cbind(d1,
        parameters::demean(d1, select = c("anx", "ch", "bg"), group = "country"))

hist(d1$anx)
```

@@

```{r}
library("ggdag")
library("dagitty")
dg1a <- dagify(
  anx  ~ belief + church + male + country + U,
  belief ~ age + male + country + church + U,
  church ~ age + male + country + U,
  ses ~ country + age + edu,
  edu ~ country + male, 
  U ~ age + ses + country,
  exposure =  "belief",
  outcome =   "anx",
  latent = "U",
  labels = c(
    "belief" = "belief God",
    "church" = "religious service attendance",
    "anx" = "anxiety",
    "edu" = "education",
    "ses" = "SES",
    "male" = "male",
    "country" = "country",
    "age" = "age",
    "U" = "Unmeasured
    distressing life events"
  )
) #%>%
 # tidy_dagitty()

d0a <-ggdag::ggdag(dg1a, text = FALSE, use_labels = "label")  + theme_dag() + ggtitle("What if we were to assume distressing events increase belief in God?")
d0a
# graph adjustment sets

d1a<-ggdag::ggdag_adjustment_set(dg1a, node_size = 14, text = FALSE, use_labels = "label") +
  theme(legend.position = "bottom") +
  theme_dag() + ggtitle("If we assume distressing events affect belief and service we cannot estimate causal effects ")

d1a

dg1 <- dagify(
  anx  ~ belief + church + male + country + U,
  belief ~ age + male + country + church + U,
  church ~ age + male + country + U,
  ses ~ country + age + edu,
  edu ~ country + male, 
  U ~ age + ses + country,
  exposure =  "belief",
  outcome =   "anx",
  latent = "U",
  labels = c(
    "belief" = "belief God",
    "church" = "religious service attendance",
    "anx" = "anxiety",
    "edu" = "education",
    "ses" = "SES",
    "male" = "male",
    "country" = "country",
    "age" = "age",
    "U" = "Unmeasured
    distressing life events",
    coords = list(x = c(anx =6 , 
                        belief = 5, 
                        church = 4, 
                        ses = 3,
                        male = 2, 
                        age = 2,
                        country = 2,
                        U = 1),
                  y = c(anx = 2, 
                        belief = 2, 
                        church = 2, 
                        ses = 2,
                        male = 2, 
                        age = 2,
                        country = 1,
                        U = 1)) #%>%#%>%
 # tidy_dagitty()       
# 
dp0 <-ggdag::ggdag(dg1, text = FALSE, use_labels = "label")  + theme_dag() + ggtitle("Assumed unmeasured causal effects of distressing experiences")

dp0
# # graph adjustment sets
# 
#dp1<-ggdag::ggdag_adjustment_set(dg1, node_size = 14, text = FALSE, use_labels = "label") +
#   theme(legend.position = "bottom") +
#   theme_dag() + ggtitle("Adjustment sets for Belief in God")
#dp1
dp0
```

@@

We condition on the following model:

-   religion + ses + male + country + a different unmeasured latent variable1 (e.g. privilege) affects distress.

-   age + male + country + and unmeasured latent variable2 (e.g. parent's religion, call this U1) affects Religion

-   country + age + an unmeasured latent variable1 causes ses (citations...)

-   our "exposure" is religious service attendance or religious belief and our outcome is "anxiety"

```{r}
library("ggdag")
dg2 <- dagify( 
  anx  ~ belief + church + male + country + U,
  belief ~ age + male + country + church,
  church ~ age + male + country,
  ses ~ country + age + edu,
  edu ~ country + male, 
  U ~ age + ses + country,
  exposure =  "church",
  outcome =   "anx",
  latent = "U",
  labels = c(
    "belief" = "belief God",
    "church" = "religious service attendance",
    "anx" = "anxiety",
    "edu" = "education",
    "ses" = "SES",
    "male" = "male",
    "country" = "country",
    "age" = "age",
    "U" = "Unmeasured
    distressing life events"
  )
) %>%
  tidy_dagitty()

ggdag::ggdag(dg2) + theme_dag()

nocause <- ggdag::ggdag(dg2, text = FALSE, use_labels = "label")  + theme_dag() + labs(title = "Assume unmeasured distressing experience does not affect Belief or Service")
nocause

dg0<-ggdag::ggdag_adjustment_set(dg2, node_size = 14, text = FALSE, use_labels = "label") +
  theme(legend.position = "bottom") +
  theme_dag() + ggtitle("Adjustment set for religious service
assuming service does not change from distress")

dp0

dpz <- dagify(
  anx  ~ belief + church + male + country + U,
  belief ~ age + male + country + church,
  church ~ age + male + country,
  ses ~ country + age + edu,
  edu ~ country + male, 
  U ~ age + ses + country,
  exposure =  "belief",
  outcome =   "anx",
  latent = "U",
  labels = c(
    "belief" = "belief God",
    "church" = "religious service attendance",
    "anx" = "anxiety",
    "edu" = "education",
    "ses" = "SES",
    "male" = "male",
    "country" = "country",
    "age" = "age",
    "U" = "Unmeasured
    distressing life events"
  )
)

ggdag::ggdag(dpz) + theme_dag()

# graph adjustment sets
dg1<-ggdag::ggdag_adjustment_set(dpz, node_size = 14, text = FALSE, use_labels = "label") +
  theme(legend.position = "bottom") +
  theme_dag() + ggtitle("Adjustment set for religious belief
assuming belief does not change from distress")

dg1
```

Save image

```{r dg1, eval=FALSE}
# save graph
ggsave(
  dg1,
  path = here::here("Figs"),
  width = 10,
  height = 5,
  units = "in",
  filename = "dag_belief.jpg",
  device = 'jpeg',
  limitsize = FALSE,
  dpi = 1200
)

@@

```{r dp0, eval=FALSE}
# save graph
ggsave(
  dg1,
  path = here::here("Figs"),
  width = 10,
  height = 5,
  units = "in",
  filename = "dag_church.jpg",
  device = 'jpeg',
  limitsize = FALSE,
  dpi = 1200
)

Graph for paper

## Anxiety causes belief DAG

```{r}
dpL <- dagify(
  anx  ~  church + male + country + U,
  belief ~ age + male + country + church + anx,
  church ~ age + male + country,
  ses ~ country + age + edu,
  edu ~ country + male, 
  U ~ age + ses + country,
  exposure =  "anx",
  outcome =   "belief",
  latent = "U",
  labels = c(
    "belief" = "belief God",
    "church" = "religious service attendance",
    "anx" = "anxiety",
    "edu" = "education",
    "ses" = "SES",
    "male" = "male",
    "country" = "country",
    "age" = "age",
    "U" = "Unmeasured
    distressing life events"
  )
) %>%
  tidy_dagitty()

dl <- ggdag::ggdag(dpL, text = F, use_labels = "label") + theme_dag()
dl1<- dl + labs(title ="Assume Anxiety causes Belief in God")
dl1

dl2<-ggdag::ggdag_adjustment_set(dpL, node_size = 14, text = FALSE, use_labels = "label") +
  theme(legend.position = "bottom") +
  theme_dag() + ggtitle("Adjustment set assuming anxiety causes belief in God")
dl2

## Anxiety causes church DAG

```{r}
dpC <- dagify(
  anx  ~   male + country + U,
  belief ~ age + male + country + church + anx,
  church ~ age + male + country,
  ses ~ country + age + edu,
  edu ~ country + male, 
  U ~ age + ses + country,
  exposure =  "anx",
  outcome =   "church",
  latent = "U",
  labels = c(
    "belief" = "belief God",
    "church" = "religious service attendance",
    "anx" = "anxiety",
    "edu" = "education",
    "ses" = "SES",
    "male" = "male",
    "country" = "country",
    "age" = "age",
    "U" = "Unmeasured
    distressing life events"
  )
) %>%
  tidy_dagitty()

dC <- ggdag::ggdag(dpC, text = F, use_labels = "label") + theme_dag()
dlC<- dC + labs(title ="Assume Anxiety causes Religious Service")
dlC

dl2C<-ggdag::ggdag_adjustment_set(dpC, node_size = 14, text = FALSE, use_labels = "label") +
  theme(legend.position = "bottom") +
  theme_dag() + ggtitle("Adjustment set for Anxiety causing Religious Service")
dl2C

## Dag graph

```{r}
library(patchwork)
 (dp0 + d1a)/   (nocause + dg1 + dp2)  /(dl1 + dl2 + dl2C)+   plot_layout(guides = 'collect')  + plot_annotation(title = 'Three causal models', tag_levels = "a") 
# dag_ful 20/20
```

### correlation

```{r}
correlation::correlation(d1, select = "ch_s",select2 = "bg_s")

correlation::correlation(d1, select = "bg_s",select2 = "anx")

correlation::correlation(d1, select = "ch_s",select2 = "anx")

```{r}
library(lme4)
```

### Check LMER Results

```{r}
library(patchwork)
mlmerCH <- lmer(
    anx ~
    #bg_s +
    ch_s +
    age_s  +
    male +
    ( 1 + ch_s | country), 
  data = d1)

sjPlot::tab_model(mlmerCH)

mlmerBG <- lmer(
    anx ~
    bg_s +
    ch_s +
    age_s  +
    male +
    ( 1 + bg_s | country), 
  data = d1)

sjPlot::tab_model(mlmerBG)
```

## General Estimating Equations

### IPW Anxiety \~ Belief

First check for imbalance using the cobolt package.

```{r}
# CHECK BALANCE
# test
cobalt::bal.tab(bg_s ~ age_s  + male + country,
        data = d1, estimand = "ATE", m.threshold = .05)
```

Get inverse probability weights

```{r}
w_out_bs <- weightit(bg_s ~ age_s  +ch_s +  male + country,
        data = d1, estimand = "ATE", method = "ebal", stabilize = TRUE)
w_out_bs

summary(w_out_bs)
sum(w_out_bs$weights)

cobalt::bal.tab(w_out_bs, m.threshold = .05, disp.v.ratio = TRUE)
```

```{r}
library("ipw")
d1ipwB <- ipw::ipwpoint(
  exposure = bg_s,
  family = "gaussian",
  numerator = ~ 1,
  denominator = ~  ch_s + age_s  + male + country,
  data = as.data.frame(d1)
)

summary(d1ipwB$ipw.weights)
sum(d1ipwB$ipw.weights >= 10)

d1pB <- d1 %>% 
  mutate(ipw = w_out_bs$weights) %>%
  filter(d1ipwB$ipw.weights < 10)

Model:

```{r}
mgeeB  <- geeglm(
  anx ~
    bg_s,# already weighted
   # ch_s +
   # age_s  +
   # male,
  data = d1pB,
  id = country,
  corstr = "exchangeable",
  weights = ipw
)
mgeeB

parameters::model_parameters(mgeeB) %>%
  print_html()

library(ggeffects)
p0BG <- plot(ggeffects::ggemmeans(mgeeB, terms = "bg_s [all]"), add.data = TRUE, dot.alpha = 0.1)    # 
p0BG 
```

### IPW Anxiety \~ Church

First we create Inverse Probability Weights

```{r}
library("ipw")

d1ipw <- ipw::ipwpoint(
  exposure = ch_s,
  family = "gaussian",
  numerator = ~ 1,
  denominator = ~  age_s  + male + country,
  data = as.data.frame(d1)
)

summary(d1ipw$ipw.weights)
sum(d1ipw$ipw.weights > 10)

d1p <- d1 %>% 
  mutate(ipw = d1ipw$ipw.weights) %>%
  filter(ipw < 10)
```

Model

```{r}
mgeeCH <- geeglm(
  anx ~
    ch_s,# + # already weighted
    #age_s  +
  #  male,
  data = d1p,
  id = country,
  weights = ipw
)

parameters::model_parameters(mgeeCH) %>%
  print_html()

library(ggeffects)
pmgeeCH <- plot(ggeffects::ggemmeans(mgeeCH, terms = "ch_s [all]"), add.data = TRUE, dot.alpha = 0.1)    # 
pmgeeCH
```

Model with with trimmed IPW (as recommended to avoid leverage from rare cases). Note, the result here is the same.

```{r, eval = FALSE}
# trim IPW to less than 10 
d1pf <- d1 %>% 
  mutate(ipw = d1ipw$ipw.weights) %>%
  filter(ipw < 10)

m0f <- geeglm(
  anx ~
    ch_s,# +
    #age_s  +
  #  male,
  data = d1pf,
  id = country,
  weights = ipw
)

parameters::model_parameters(m0f) %>%
  print_html()

library(ggeffects)
p0f <- plot(ggeffects::ggemmeans(m0f, terms = "ch_s [all]"), add.data = TRUE, dot.alpha = 0.1)    # 
p0f
```

## Results summary Anxiety \~ Belief

```{r}
m1 <- brm( 
  anx ~
    bg_s +
    ch_s +
    age_s  +
    male +
    (1 + bg_s | country),
  data = d1,
  family = cumulative(link = "logit"),
  seed = 1234,
  warmup = 1000,
  iter = 3000,
  chains = 4,
  file = here::here("models", "m2o_real")
)

parameters::model_parameters(m1, test = "p_direction")
brms::ranef(m1)

parameters::parameters(
  m1,
  test = "pd",
  priors = FALSE, 
  effects = "all",
  drop = TRUE,
  group_level = FALSE,
  diagnostic = "Rhat") %>%
    mutate_if(is.numeric, ~ round(., 2)) %>%
    mutate_all(funs(str_replace(., "b_", ""))) %>%
    kable(booktabs = T, "latex", caption =  "Parameter estimates for model of Belief on Anxiety") %>%
    print()

>>>>

```{r runanalysis, echo=FALSE, include = FALSE}
# source("libs.R") # libraries 
# source("funs.R") # custom functions
library("tidyverse")
library("easystats")
library("ggplot2") #plots
#library("sjstats") #test statistics
#library("sjPlot")
#library("sjmisc")
##library("insight")
#library("see")
#library("performance")
library("ggraph")
#library("parameters")
library("lme4")
#library("psych") ## correlation matrix
library("table1")
library("ggeffects")
#library("gghighlight")
#library("texreg")
library("kableExtra")
#library("naniar") # missingness
library("Amelia")
#library("magrittr")
library("patchwork")
library("texreg")
library("viridisLite")
library("patchwork")
library("here")
#library("rethinking")
#library("statsExpressions")
#library("ggstatsplot")
library("ggthemes")
=library("rstan")
library("brms")
library("tidybayes")
library("bayesplot")
library("dagitty")
library("ggdag")
library("geepack")  # marginal structural models
library("ipw") # inverse probability weighting. 
library("WeightIt")# inverse probability weighting. 
rstan_options(auto_write=TRUE)
options(mc.cores=parallel::detectCores ())
theme_set(theme_few())
```

@@

```{r}
# get data into shape

d1 <- df %>%
  dplyr::filter(
   #  !is.na(wb_psychANXIETY),
   #  !is.na(age),
   #  !is.na(rel_CHURCHFREQ),
   # # !is.na(wb_psychMEANING),
   #  !is.na(male),
   #  !is.na(rel_EXTENTBELIEVEGOD),
  ) %>%
  dplyr::mutate(
    anx = as.integer(6- wb_psychANXIETY), # reverse coded! rescale 1-5
    #anx_s = scale(anx),
    #put outcome in ST units (see McElreath 2021)  # not necessary
    #age_s = scale(age),
    ch = rel_CHURCHFREQ,
  #  mn  = wb_psychMEANING,
    edu = education,
    bg =  rel_EXTENTBELIEVEGOD#,
  #  ch_s = scale(rel_CHURCHFREQ),
  #  mn_s = scale(wb_psychMEANING),
   # bg_s = scale(rel_EXTENTBELIEVEGOD)
  ) %>%
  dplyr::select(anx,
                ch,
                age,
                ses,
                #    mn,
                edu,
                bg,
                # anx_s,
                # age_s,
                #  ch_s,
                #  mn_s,
                edu,
                country,
                male,
                #   bg_s,
                wb_psychANXIETY)

@@

```{r}
library("ggdag")
library("dagitty")
dg1a <- dagify(
  anx  ~ belief + church  + age + male + ses + country ,
  belief ~ age + church + male + edu + ses  + church + country,
  church ~ age + male + edu + ses + country,
  ses ~ country + age + edu,
  edu ~ country + male + age, 
 # U ~ age + ses + country,
  exposure =  "belief",
  outcome =   "anx",
 # latent = "U",
  labels = c(
    "belief" = "belief God",
    "church" = "religious service attendance",
    "anx" = "anxiety",
    "edu" = "education",
    "ses" = "SES",
    "male" = "male",
    "country" = "country",
    "age" = "age",
    "U" = "Unmeasured
    distressing life events"
  )
)     
dg1a
print( impliedConditionalIndependencies( dg1a ) )
print( adjustmentSets( dg1a,  "belief","anx" ) )

# 
# d0a <-ggdag::ggdag(dg1a, text = FALSE, use_labels = "label")  + theme_dag() + ggtitle("What if we were to assume distressing events increase belief in God?")
# d0a
# # graph adjustment sets
# 
# d1a<-ggdag::ggdag_adjustment_set(dg1a, node_size = 14, text = FALSE, use_labels = "label") +
#   theme(legend.position = "bottom") +
#   theme_dag() + ggtitle("If we assume distressing events affect belief and service we cannot estimate causal effects ")
# 
# d1a 
# 
# 
# # 
# dp0 <-ggdag::ggdag(dg1, text = FALSE, use_labels = "label")  + theme_dag() + ggtitle("Assumed unmeasured causal effects of distressing experiences")
# 
# dp0
# # # graph adjustment sets
# # 
# #dp1<-ggdag::ggdag_adjustment_set(dg1, node_size = 14, text = FALSE, use_labels = "label") +
# #   theme(legend.position = "bottom") +
# #   theme_dag() + ggtitle("Adjustment sets for Belief in God")
# #dp1
# dp0
```
'
We adjust for: { church, country, male, ses } . Because we do not have information about education, we condition on the ladder

@@

```{r}
library("ggdag")
dg2 <- dagify( 
  anx  ~ belief + church  + age + male + ses + country ,
  belief ~ age + church + male + edu + ses  + church + country,
  church ~ age + male + edu + ses + country,
  ses ~ country + age + edu,
  edu ~ country + male + age, 
  exposure =  "church",
  outcome =   "anx",
#  latent = "U",
  labels = c(
    "belief" = "belief God",
    "church" = "religious service attendance",
    "anx" = "anxiety",
    "edu" = "education",
    "ses" = "SES",
    "male" = "male",
    "country" = "country",
    "age" = "age",
    "U" = "Unmeasured
    distressing life events"
  )
)

%>%
  tidy_dagitty()

print( impliedConditionalIndependencies( dg2 ) )
print( adjustmentSets( dg1a,  "church", "anx" ) )

# 
# ggdag::ggdag(dg2) + theme_dag()
# 
# nocause <- ggdag::ggdag(dg2, text = FALSE, use_labels = "label")  + theme_dag() + labs(title = "Assume unmeasured distressing experience does not affect Belief or Service")
# nocause
# 
# dg0<-ggdag::ggdag_adjustment_set(dg2, node_size = 14, text = FALSE, use_labels = "label") +
#   theme(legend.position = "bottom") +
#   theme_dag() + ggtitle("Adjustment set for religious service
# assuming service does not change from distress")
# 
# dp0
# 
# 
# dpz <- dagify(
#   anx  ~ belief + church + male + country + U,
#   belief ~ age + male + country + church,
#   church ~ age + male + country,
#   ses ~ country + age + edu,
#   edu ~ country + male, 
#   U ~ age + ses + country,
#   exposure =  "belief",
#   outcome =   "anx",
#   latent = "U",
#   labels = c(
#     "belief" = "belief God",
#     "church" = "religious service attendance",
#     "anx" = "anxiety",
#     "edu" = "education",
#     "ses" = "SES",
#     "male" = "male",
#     "country" = "country",
#     "age" = "age",
#     "U" = "Unmeasured
#     distressing life events"
#   )
# )
# 
# ggdag::ggdag(dpz) + theme_dag()
# 
# 
# # graph adjustment sets
# dg1<-ggdag::ggdag_adjustment_set(dpz, node_size = 14, text = FALSE, use_labels = "label") +
#   theme(legend.position = "bottom") +
#   theme_dag() + ggtitle("Adjustment set for religious belief
# assuming belief does not change from distress")
# 
# dg1
```

We have two adjustment sets: { age, church, country, male, ses } and { church, country, edu, male, ses }

<!-- ```{r dg1, eval=FALSE} -->
<!-- # save graph -->
<!-- ggsave( -->
<!--   dg1, -->
<!--   path = here::here("Figs"), -->
<!--   width = 10, -->
<!--   height = 5, -->
<!--   units = "in", -->
<!--   filename = "dag_belief.jpg", -->
<!--   device = 'jpeg', -->
<!--   limitsize = FALSE, -->
<!--   dpi = 1200 -->
<!-- ) -->

<!-- ```{r dp0, eval=FALSE} -->
<!-- # save graph -->
<!-- ggsave( -->
<!--   dg1, -->
<!--   path = here::here("Figs"), -->
<!--   width = 10, -->
<!--   height = 5, -->
<!--   units = "in", -->
<!--   filename = "dag_church.jpg", -->
<!--   device = 'jpeg', -->
<!--   limitsize = FALSE, -->
<!--   dpi = 1200 -->
<!-- ) -->

## Multiple imputation

### Visualise missing data

```{r cache = TRUE}
library("naniar")
vis_miss(df) # substantial pattern of missingness in a few variables, 
df
df$wb_soc_3
dff<-df%>%
  select(-wb_soc_3)
sum(is.na(df$education))

miss_graph<- gg_miss_upset(dff)
miss_graph
# save graph
ggsave(
  dg1,
  path = here::here("Figs"),
  width = 10,
  height = 5,
  units = "in",
  filename = "dag_church.jpg",
  device = 'jpeg',
  limitsize = FALSE,
  dpi = 1200
)

library(Amelia)

  # x is the longitudional dataframe (here 'd_3')
set.seed(1234)
prep <- d1 %>% # Remove what we do not need anymore
    arrange(country) %>%
    dplyr::select(anx,
                  ch,
                  age,
                  edu,
                  bg,
                  edu,
                  country,
                  male,
                  anx, 
                  ses)
# impute missing
prep <- as.data.frame(prep) # tibble won't run in amelia
set.seed(1234)
prep2 <- Amelia::amelia(
  prep,
  #dataset to impute
  m = 10,
  # number of imputations
  cs = c("country"),
  #ts = c("years"),
  noms = c(
    "male"
  ))
  #idvars = c("country")#,
  # not imputing outcomes
 # polytime = 3
)  #https://stackoverflow.com/questions/56218702/missing-data-warning-r

out <- Amelia::transform.amelia(
  prep2,
  age_s = scale(age),
  bg_s = scale(bg),
  anx_s = scale(anx),
  age_s = scale(age),
  ch_s =scale(ch),
  edu_s = scale(edu),
  ses_s = scale(ses),
  male_2 = scale(as.numeric(male))/2) # scale by 2 sds

#saveRDS(out, here::here("mods","out"))
out <-readRDS(here::here("mods","out"))
```

We find there is substantial missingness in denomination. There is also missingness in ethnicity. Overall missingness is low in other indicators. However, 
Because missingness can introduce bias, we multiply impute responses.

## Model for belief

### gee

```{r}
##
#{ age, country, edu, male, ses }
m<-10
models<-NULL
for(i in 1:m) {
  models[[i]]  <- geeglm(
  anx_s ~ bg_s + ch_s + age_s + edu_s + male_2 + ses_s,
  data = out$imputations[[i]],  
  id = country,
  corstr = "exchangeable"
)
}

# saveRDS(models, here::here(
#   "mods","models.rds")
# )

parameters::pool_parameters(models)

pred <- ggeffects::ggemmeans(models[[1]], terms = c("bg_s[all]"))
pred

plot(pred,
     add.data=T,dot.alpha=.1, 
     facets = F)  + #scale_y_continuous(limits=c(-.5,.5)) + 
  theme_classic() + ggtitle("") # title to be suppled
```

### Marginal structural model Church

```{r}
library(mice)
d2<-mice(d1)
d3<-complete(d2)
saveRDS(d3,here::here("mods","d3"))
d3 <-readRDS(here::here("mods","d3"))
d4<-d3%>%
  select(anx, ch, bg, age, edu,male,ses,country)%>%
  drop_na()%>%
  mutate(anx_s = scale(anx),
         bg_s = scale(bg),
         ch_s = scale(ch),
         age_s = scale(age),
         edu_s = scale(edu),
         ses_s = scale(ses),
         male_2 =scale(as.numeric(male))/2,
         ses_s = scale(ses),
         country=as.factor(country))

m<-10
modelsCH<-NULL
for(i in 1:m) {
  modelsCH[[i]]  <- geeglm(
  anx_s ~  ch_s + age_s + edu_s + male_2 + ses_s,
  data = out$imputations[[i]],  
  id = country,
  corstr = "exchangeable"
)
}

saveRDS(modelsCH, here::here(
  "mods","modelsCH.rds")
)

pred <- ggeffects::ggemmeans(modelsCH[[1]], terms = c("ch_s[all]"))
pred

plot(pred,
    # add.data=T,dot.alpha=.1, 
     facets = F)  + scale_y_continuous(limits=c(-.5,.5)) + theme_classic() + ggtitle("") # title to be suppled
parameters::pool_parameters(modelsCH)

parameters::pool_parameters(modelsCH)
#parameters::pool_parameters(modelschG)

library(ipw)

dbl <- ipw::ipwpoint(
  exposure = bg_g,
  family = "gaussian",
  numerator = ~ 1,
  denominator = ~ age_s +ch_s + edu_s + male_2 + ses_s + country,
  trunc = 0.01,
  data = as.data.frame(d4)
)

dch <- ipw::ipwpoint(
  exposure = ch_s,
  family = "gaussian",
  numerator = ~ 1,
  denominator = ~ age_s + edu_s + male_2 + ses_s + country,
  trunc = 0.01,
  data = as.data.frame(d4)
)

d1p <- d4 %>% 
  mutate(ipwCH = dch$weights.trunc,
         ipwBG = dbl$weights.trunc)

max(d1p$ipwBG)
max(d1p$ipwCH)
```

```{r}

ipb_bg<- geeglm(
  anx_s ~ bg_s,
  data = d1p,  
  id = country,
  corstr = "exchangeable",
  weights = ipwBG
)

ipb_ch<- geeglm(
  anx_s ~  ch_s,
  data = d1p,  
  id = country,
  corstr = "exchangeable",
  weights = ipwCH
)

model_parameters(ipb_bg)

model_parameters(ipb_ch)

library(EValue)

# sensitivity = Church
evalues.OLS(-0.08, se = 0.01, sd = 1, delta = 1)

# sensitivity
evalues.OLS(0.04, se = 0.01, sd = 1, delta = 1)

bias_plot(1.3009531, xmax = 6)

# An E-value for unmeasured confounding is minimum strength of association, on the risk ratio scale, that unmeasured confounder(s) would need to have with both the treatment and the outcome to fully explain away a specific treatment–outcome association, conditional on the measured covariates.
# 
# The estimate is converted appropriately before the E-value is calculated. See conversion functions for more details. The point estimate and confidence limits after conversion are returned, as is the E-value for the point estimate and the confidence limit closest to the proposed "true" value (by default, the null value.)
# 
# For an OLS() estimate, the E-value is for linear regression with a continuous exposure and outcome. Regarding the continuous exposure, the choice of delta defines essentially a dichotomization in the exposure between hypothetical groups of subjects with exposures equal to an arbitrary value c versus to another hypothetical group with exposures equal to c + delta.
# 
# For example, if resulting E-value is 2, this means that unmeasured confounder(s) would need to double the probability of a subject's having exposure equal to c + delta instead of c, and would also need to double the probability of being high versus low on the outcome, in which the cutoff for "high" versus "low" is arbitrary subject to some distributional assumptions (Chinn, 2000).
```

Adjusted GEE no weights

```{r}

ipb_bg_noweights <- geeglm(
  anx_s ~ bg_s + ch_s + age_s + edu_s + male_2 + ses_s,
  data = d1p,  
  id = country,
  corstr = "exchangeable"
)

ipb_ch_noweights <- geeglm(
  anx_s ~ ch_s + age_s + edu_s + male_2 + ses_s,
  data = d1p,  
  id = country,
  corstr = "exchangeable"
)

model_parameters(ipb_bg_noweights)
model_parameters(ipb_bg)

model_parameters(ipb_ch_noweights)
model_parameters(ipb_ch)
```

We note that the multi-level models give different estimates.

### GlMM TMB BELIEF

```{r}
library(glmmTMB)
m<-10
modelsb<-NULL
for(i in 1:m) {
  modelsb[[i]]  <- glmmTMB(anx_s ~ bg_s + ch_s + age_s + edu_s + male_2 + ses_s + 
                            (1+ bg_s|country), 
                              data = out$imputations[[i]],
                              family =)
}

parameters::pool_parameters(modelsb)

pred <- ggeffects::ggemmeans(modelsb[[1]], terms = c("bg_s[all]"))
pred

plot(pred,
    # add.data=T,dot.alpha=.1, 
     facets = F)  + scale_y_continuous(limits=c(-.2,.2)) + theme_classic() + ggtitle("") # title to be suppled
```

### GlMM TMB CHURCH

```{r}
library(glmmTMB)
m<-10
modelsC<-NULL
for(i in 1:m) {
  modelsC[[i]]  <- glmmTMB(anx_s ~  ch_s + age_s + edu_s + male_2 + ses_s + 
                            (1+ bg_s|country), 
                              data = out$imputations[[i]],
                              family =)
}

parameters::pool_parameters(modelsC)

pred <- ggeffects::ggemmeans(modelsC[[1]], terms = c("ch_s[all]"))
pred

plot(pred,
     add.data=T,dot.alpha=.05, 
     facets = F)  + theme_classic() + ggtitle("") # title to be suppled
```

### Test implied conditional independence

```{R}
m<-10
models<-NULL
for(i in 1:m) {
  models[[i]] <- lmer(anx_s ~ 
                        bg_s + 
                        ch_s + 
                        age_s + 
                        edu_s + 
                        male_2 + 
                        ses_s + 
                        (1+ bg_s|country ), data=out$imputations[[i]])
}

parameters::pool_parameters(models,
                            component = "marginal")

pred <- ggeffects::ggemmeans(models[[1]], terms = c("bg_s[all]"))
pred

plot(pred,
    # add.data=T,dot.alpha=.1, 
     facets = F)  + scale_y_continuous(limits=c(-.2,.2)) + theme_classic() + ggtitle("") # title to be suppled

listout <- list(
  out$imputations$imp1,
  out$imputations$imp2,
  out$imputations$imp3,
  out$imputations$imp4,
  out$imputations$imp5,
  out$imputations$imp6,
  out$imputations$imp7,
  out$imputations$imp8,
  out$imputations$imp9,
  out$imputations$imp10
)
#saveRDS(listout, here::here("mods", "listout"))
listout<- readRDS( here::here("mods", "listout"))

m_bg <- brm_multiple( 
  anx_s ~
    bg_s +
    ch_s +
    age_s +
    edu_s +
    male_2 +
    ses_s +
    (1 + bg_s | country),
  data = listout,
  seed = 1234,
  warmup = 1000,
  iter = 2000,
  chains = 4,
  backend = "cmdstanr", 
  threads = threading(4),
  file = here::here("mods", "m_bg")
)

parameters::model_parameters(m_bg, test = "p_direction")
brms::ranef(m_bg)

parameters::parameters(
  m_bg,
  test = "pd",
  priors = FALSE, 
  effects = "all",
  drop = TRUE,
  group_level = FALSE,
  diagnostic = "Rhat") %>%
    mutate_if(is.numeric, ~ round(., 2)) %>%
    mutate_all(funs(str_replace(., "b_", ""))) %>%
    kable(booktabs = T, "latex", caption =  "Parameter estimates for model of Belief on Anxiety") %>%
    print()

@@

### Bayesian Church Attendaance

```{r}

listout <- readRDS(here::here("mods","listout"))
modmc <- brm_multiple(
  anx_s ~ ch_s + age_s + edu_s + male_2 +ses_s + (1 + ch_s | country),
  data = listout,
  seed = 1234,
  warmup = 1000,
  iter = 2000,
  chains = 4,
  backend = "cmdstanr",
  threads = threading(4)
)

#saveRDS(modmc, here::here("mods", "modmc.rds"))
summary(modmc)
```

### Summary of selection bias

```{r}
set.seed(1234)
y<- rnorm(1000,0,1)
a<- rnorm(1000,0,1)
s<- rnorm(1000, a -(2*y),4)

dlbind <-data.frame(y,a,s)
summary(lm(y ~  a + s, data = dlbind))
```
